quollr: An R Package for Visualizing $2-D$ Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-05-07 paper-quollr.Rmd
Added layouts for example
Started updating according to the package updates

@@

The development version can be installed from GitHub:

@@

@@

@@

The algorithm begins by scaling NLDR data to a standard scale using the `gen_scaled_data()` function. This function standardizes the data and provides the original limits of embeddings and the aspect ratio.

```{r, echo=TRUE}
scaled_nldr_obj_scurve <- gen_scaled_data(data = s_curve_noise_umap)

s_curve_noise_umap_scaled <- scaled_nldr_obj_scurve$scaled_nldr

lim1 <- scaled_nldr_obj_scurve$lim1
lim2 <- scaled_nldr_obj_scurve$lim2
r2 <- diff(lim2)/diff(lim1) 
```

>>>>

## Installation

@@

and the development version can be installed from GitHub:

@@

## Web site

More documentation of the package can be found at the web site [https://jayanilakshika.github.io/quollr/](https://jayanilakshika.github.io/quollr/).

@@

Add a table of data sets that quollr have

@@

The algorithm begins by scaling NLDR data to a standard scale using the `gen_scaled_data()` function. This function standardizes the data with first embedding scale to 0 and 1, The second embedding scales to 0 and the maximum of the second embedding. The resulting output provides the scaled NLDR data and the original limits of embeddings.

```{r, echo=TRUE}
scurve_nldr_obj <- gen_scaled_data(nldr_data = scurve_umap)

scurve_nldr_obj
```

```{r, echo=TRUE}
scurve_umap_scaled <- scurve_nldr_obj$scaled_nldr

lim1 <- scurve_nldr_obj$lim1
lim2 <- scurve_nldr_obj$lim2
r2 <- diff(lim2)/diff(lim1) 
```

We can compute the `r2` which is the ratio of the ranges of the original embedding components.
